%-------------------------
% Full-Stack Resume for Yash Agarwal (Revised)
%-------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref} % hidelinks for a clean look, links are still clickable
\usepackage{fancyhdr}
\input{glyphtounicode}
\pagestyle{fancy}\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}\addtolength{\textheight}{1.0in}
\urlstyle{same}\raggedbottom\raggedright\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\titlerule\vspace{-5pt}]
\pdfgentounicode=1

%--- Commands ---
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2\\
    \textit{\small#3} & \textit{\small#4}\\
  \end{tabular*}\vspace{-7pt}}
% Modified resumeProjectHeading to consistently use "Live Demo" for project links
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \href{#2}{Live Demo} \\
  \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%--- Heading ---
\begin{center}
  \textbf{\Huge \scshape Yash Agarwal}\\
  \small
  \href{mailto:190e785@gmail.com}{190e785@gmail.com} \textbar\ +91-90276-01476 \textbar\ \href{<LinkedIn_URL>}{LinkedIn} \textbar\ \href{<GitHub_URL>}{GitHub}
\end{center}

%--- Education ---
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Graphic Era Hill University}{Uttarakhand, India}
    {B.Tech, CSE (Honors in ML \& AI)}{Aug 2023 -- Jul 2027}
\resumeSubHeadingListEnd

%--- Projects ---
\section{Projects}
\resumeSubHeadingListStart

  % Interactive Resume Maker (Frontend)
  \resumeProjectHeading{Interactive Resume Maker}{<Interactive_Resume_Maker_URL>}
  \resumeItemListStart
    \resumeItem{Developed a dynamic résumé editor with React and Tailwind CSS, enabling real-time section edits.}
    \resumeItem{Integrated serverless PDF export via Puppeteer, ensuring high-fidelity document generation.}
    \resumeItem{Implemented drag-and-drop section reordering and theme customization for user flexibility.}
    \resumeItem{Conducted usability testing and iterated UI to meet ARIA accessibility standards.}
    \resumeItem{Documented API endpoints and component library usage for future contributions.}
  \resumeItemListEnd

  % First Link Rule Frontend
  \resumeProjectHeading{First Link Rule Frontend}{<First_Link_Frontend_URL>}
  \resumeItemListStart
    \resumeItem{Built a Vue.js application to visualize Wikipedia first-link traversals toward \textit{"Philosophy"}.}
    \resumeItem{Rendered interactive SVG graphs and provided search/filter to inspect link paths.}
    \resumeItem{Optimized performance using code splitting and lazy loading, reducing initial payload by 40\%.}
    \resumeItem{Shared design tokens and component guidelines in a published style guide.}
    \resumeItem{Collaborated with backend team to integrate REST endpoints for real-time updates.}
  \resumeItemListEnd

  % First Link Backend (merged with relevant details)
  \resumeProjectHeading{First Link Backend}{<First_Link_Backend_URL>}
  \resumeItemListStart
    \resumeItem{Designed RESTful API with Node.js \& Express to retrieve Wikipedia first-link traversals, converting scraper from Selenium to BeautifulSoup for environment constraints.}
    \resumeItem{Stored graph data in MongoDB and implemented Redis caching for performance.}
    \resumeItem{Secured endpoints via JWT authentication and rate limiting for abuse prevention.}
    \resumeItem{Containerized service with Docker and established CI/CD pipeline for automated deployments to AWS Lambda behind API Gateway, achieving on-demand scalability.}
    \resumeItem{Monitored performance and logs via Render.com and Grafana dashboards.}
    \resumeItem{Wrote comprehensive API documentation, integrated Swagger UI for developers, and ensured API contract consistency with the frontend team.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%--- Skills ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in,label={}]
  \small{\item{
    \textbf{Frontend:} React, Vue.js, Vite, Tailwind CSS, HTML5, CSS3, ES6\\
    \textbf{State Mgmt:} Redux, Vuex, Context API\\
    \textbf{Backend:} Node.js, Express, Flask, FastAPI, RESTful APIs\\
    \textbf{Databases:} MongoDB, PostgreSQL, Redis\\
    \textbf{DevOps:} Docker, AWS Lambda, API Gateway, CI/CD (GitHub Actions), Vercel, Webpack, Lighthouse, Render.com, Grafana\\
    \textbf{Security:} JWT, OAuth2, Helmet, Bedrock Passport\\
    \textbf{Tools:} Git, npm/yarn, Puppeteer, BeautifulSoup\\
    \textbf{Design:} Figma, Adobe XD, responsive \& accessible UI
  }}
\end{itemize}

%--- Certifications ---
\section{Certifications}
\resumeSubHeadingListStart
  \resumeItem{AWS Certified Cloud Practitioner}
  \resumeItem{AWS Solutions Architect -- Associate}
  \resumeItem{AWS Certified Developer -- Associate}
  \resumeItem{Designing Event-Driven Architectures}
  \resumeItem{Google Cloud Certified Associate Cloud Engineer}
\resumeSubHeadingListEnd

\end{document}