\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\input{glyphtounicode}
\pagestyle{fancy}\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}\addtolength{\textheight}{1.0in}
\urlstyle{same}\raggedbottom\raggedright\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\titlerule\vspace{-5pt}]
\pdfgentounicode=1

%--- Commands ---
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[3]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} & {\small #3} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%--- Heading ---
\begin{center}
  \textbf{\Huge \scshape Yash Agarwal}\\
  \small
  \href{mailto:190e785@gmail.com}{190e785@gmail.com} \textbar\ +91-90276-01476 \textbar\ 
  \href{https://in.linkedin.com/in/yash-agarwal-190e785}{LinkedIn} \textbar\ 
  \href{https://github.com/190-785}{GitHub}
\end{center}

%--- Education ---
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Graphic Era Hill University}{Uttarakhand, India}
    {Bachelor of Technology in Computer Science \& Engineering (Honors in ML \& AI)}{Aug 2023 -- July 2027}
\resumeSubHeadingListEnd

%--- Projects ---
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {https://github.com/190-785/Interactive-Resume-Maker}{Interactive Resume Maker}{April 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Developed a dynamic resume editor using React and Tailwind CSS with real-time component editing.}
    \resumeItem{Implemented drag-and-drop reordering and multi-section expansion for intuitive layout control.}
    \resumeItem{Integrated Puppeteer-based PDF export to generate polished, print-ready resumes with custom headers and footers.}
    \resumeItem{Implemented password-based authentication and secure REST endpoints in Node.js \& Express, using JWT tokens and MongoDB for user and resume storage.}
    \resumeItem{Configured MongoDB Atlas for resume data persistence, enabling users to save and retrieve multiple resume versions.}
    \resumeItem{Leveraged React Context API and Hooks for scalable state management and optimized load times with code-splitting.}
  \resumeItemListEnd

  \resumeProjectHeading
    {https://190e785.wordpress.com/}{Personal Blog Site}{March 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Built and customized a personal blog using WordPress, custom PHP templates, and JavaScript.}
    \resumeItem{Applied SEO best practices and performance optimizations like lazy-loading and deferred scripts.}
    \resumeItem{Created reusable Gutenberg blocks for standardized tutorials and content.}
  \resumeItemListEnd

  \resumeProjectHeading
    {https://wikipedialinkrule.vercel.app}{First Link Rule (Frontend)}{August 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Built a responsive SPA using Vue.js and Tailwind CSS to visualize Wikipedia’s first-link paths.}
    \resumeItem{Integrated dynamic SVG graphs with live data fetched from a Node.js backend.}
    \resumeItem{Implemented client-side search, filter, and navigation features for interactive exploration.}
  \resumeItemListEnd

  \resumeProjectHeading
    {https://github.com/190-785/First_Link_Backend}{First Link Rule (Backend)}{August 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Built a RESTful API in Node.js \& Express that scrapes Wikipedia first-link paths using BeautifulSoup.}
    \resumeItem{Used MongoDB for traversal data storage and Redis for caching to improve performance.}
    \resumeItem{Dockerized the backend and deployed on Render and AWS Lambda for scalable access.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%--- Skills ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in,label={}]
  \small{\item{
    \textbf{Languages/Frameworks:} Java, React.js, Three.js, Next.js, TypeScript, Vue.js, Tailwind CSS, HTML5, JavaScript (ES6+), CSS3 \\
    \textbf{Backend:} Node.js, Express.js, REST APIs \\
    \textbf{Databases:} MongoDB, Supabase, Firebase, PostgreSQL \\
    \textbf{Tools:} Git, Vercel, Docker, Puppeteer, BeautifulSoup
  }}
\end{itemize}

%--- Certifications ---
\section{Certifications}
\resumeSubHeadingListStart
  \resumeItem{AWS Certified Cloud Practitioner}
  \resumeItem{AWS Solutions Architect -- Associate}
  \resumeItem{Google Cloud Associate Cloud Engineer}
\resumeSubHeadingListEnd

\end{document}
