%-------------------------
% AI & ML Resume for Yash Agarwal (Updated Per Feedback)
%-------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\input{glyphtounicode}
\pagestyle{fancy}\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}\addtolength{\textheight}{1.0in}
\urlstyle{same}\raggedbottom\raggedright\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\titlerule\vspace{-5pt}]
\pdfgentounicode=1

%--- Custom Commands ---
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-7pt}}
% Hyperlinked project title + full-month timeline
\newcommand{\resumeProjectHeading}[3]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} & {\small #3} \\
  \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%--- Heading ---
\begin{center}
  \textbf{\Huge \scshape Yash Agarwal}\\
  \small
  \href{mailto:190e785@gmail.com}{190e785@gmail.com} \textbar\ +91-90276-01476 \textbar\ 
  \href{https://in.linkedin.com/in/yash-agarwal-190e785}{LinkedIn} \textbar\ 
  \href{https://github.com/190-785}{GitHub}
\end{center}

%--- Education ---
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Graphic Era Hill University}{Uttarakhand, India}
    {Bachelor of Technology in Computer Science \& Engineering (Honors in ML \& AI)}{August 2023 -- July 2027}
\resumeSubHeadingListEnd

%--- Projects ---
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {https://github.com/190-785/AI-ML-Project-Grafest}{Kidney Stone Detection Model}{March 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Developed a binary classifier for ultrasound scans using TensorFlow and convolutional neural networks.}
    \resumeItem{Applied OpenCV preprocessing (thresholding, contour extraction) to enhance image quality.}
    \resumeItem{Employed data augmentation (rotation, scaling, flips) to improve model generalization.}
    \resumeItem{Packaged inference as a Flask + Docker endpoint and monitored performance with AWS SageMaker Model Monitor.}
    \resumeItem{Achieved a classification accuracy of 92\% through the tuning of learning rates, batch sizes, and dropout rates.}
  \resumeItemListEnd

  \resumeProjectHeading
    {https://github.com/190-785/AI-ML-Project-Grafest}{Celebrity Comment Real vs Fake Classifier}{February 2025 -- April 2025}
  \resumeItemListStart
    \resumeItem{Developed an NLP pipeline using spaCy for tokenization, lemmatization, and stopword removal.}
    \resumeItem{Compared Naive Bayes, SVM, and BiLSTM models in TensorFlow; selected BiLSTM achieving 89\% F1 score.}
    \resumeItem{Deployed as a Dockerized Flask REST API; tracked metrics and latency via Grafana.}
    \resumeItem{Validated model robustness with cross-validation and confusion matrix analysis.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%--- Skills ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in,label={}]
  \small{\item{
    \textbf{Machine Learning:} TensorFlow, scikit-learn, Keras, AWS SageMaker\\
    \textbf{Data \& Visualization:} pandas, NumPy, Matplotlib, OpenCV\\
    \textbf{NLP:} spaCy, NLTK, Hugging Face Transformers\\
    \textbf{Deployment \& DevOps:} Flask, Docker, AWS Lambda, Render, Git, GitHub Actions, CI/CD, Docker Compose, Grafana\\
    \textbf{Soft Skills:} Teamwork, Communication, Problem-solving
  }}
\end{itemize}

%--- Certifications ---
\section{Certifications}
\resumeSubHeadingListStart
  \resumeItem{AWS Certified Machine Learning – Specialty}
  \resumeItem{AWS ML Engineer Associate Learning Path}
  \resumeItem{AWS Cloud Quest: Machine Learning}
  \resumeItem{AWS Cloud Practitioner Essentials}
  \resumeItem{Machine Learning Essentials for Business and Technical Decision Makers}
  \resumeItem{AWS ML Engineer 4.3: Secure AWS ML Resources}
\resumeSubHeadingListEnd

\end{document}
