\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\input{glyphtounicode}
\pagestyle{fancy}\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}\addtolength{\textheight}{1.0in}
\urlstyle{same}\raggedbottom\raggedright\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\titlerule\vspace{-5pt}]
\pdfgentounicode=1

%--- Commands ---
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={} ]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%--- Heading ---
\begin{center}
  \textbf{\Huge \scshape Yash Agarwal}\\
  \small
  \href{mailto:190e785@gmail.com}{190e785@gmail.com} \textbar\ +91-90276-01476 \textbar\ 
  \href{https://in.linkedin.com/in/yash-agarwal-190e785}{LinkedIn} \textbar\ 
  \href{https://github.com/190-785}{GitHub}
\end{center}

%--- Education ---
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Graphic Era Hill University}{Uttarakhand, India}
    {B.Tech. in Computer Science \& Engineering, Honors in ML \& AI}{Aug 2023 -- July 2027}
\resumeSubHeadingListEnd

%--- Projects ---
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading{https://github.com/190-785/Interactive-Resume-Maker}{Interactive Resume Maker}
  \resumeItemListStart
    \resumeItem{Modern web app with React, Three.js, and Tailwind CSS presenting resumes in a 3D forest interface.}
    \resumeItem{Features user registration, login, and profile management secured with JWT and BCrypt password hashing.}
    \resumeItem{Real-time editing with auto-save, instant feedback, and version control stored in MongoDB.}

    \resumeItem{Responsive layout implemented with CSS flex/grid to support desktop and mobile views.}
  \resumeItemListEnd

  \resumeProjectHeading{https://github.com/190-785/Plant_Watering_System}{Plant Watering System}
  \resumeItemListStart
    \resumeItem{\textit{IO Module}: ESP8266 microcontroller reads analog soil moisture sensor to trigger water pump via threshold logic; serial console monitoring.}
    \resumeItem{\textit{WiFi Module}: ESPAsyncWebServer hosts a JSON-based configuration portal; supports OTA firmware updates.}
    \resumeItem{Logged sensor readings and pump actions to Firebase Firestore with token-based authentication.}
    \resumeItem{Configured Google Apps Script to backup data to Google Sheets for redundancy and reporting.}
  \resumeItemListEnd

  \resumeProjectHeading{https://first-link-delta.vercel.app/}{First Link Rule (Frontend)}
  \resumeItemListStart
    \resumeItem{SPA built with Vue.js and Vuex for state management to display traversal results from backend API.}
    \resumeItem{Client-side search and filter implemented with simple list rendering and pagination.}
    \resumeItem{Data fetched via Axios from REST endpoints; styled layouts using Tailwind CSS.}
  \resumeItemListEnd

  \resumeProjectHeading{https://github.com/190-785/First_Link_Backend}{First Link Rule (Backend)}
  \resumeItemListStart
    \resumeItem{Flask-based REST API using requests and BeautifulSoup to parse the first link of Wikipedia articles.}
    \resumeItem{Implements loop and dead-end detection with configurable maximum iterations.}
    \resumeItem{Persisted traversal data in MongoDB and accelerated frequent requests with Redis caching.}
    \resumeItem{Packaged services in Docker containers and deployed on AWS Lambda for scalability.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%--- Technical Skills ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in,label={}]
  \small{\item{
    \textbf{Languages:} Java, C/C++, Python, JavaScript, TypeScript \\
    \textbf{Frameworks:} React, Vue.js, Tailwind CSS, Three.js \\
    \textbf{Backend:} Node.js, Express, Flask, REST APIs \\
    \textbf{Databases:} MongoDB, PostgreSQL, Firebase \\
    \textbf{Tools:} Git, Docker, Puppeteer, BeautifulSoup, Unix/Linux \\
    \textbf{Concepts:} Data Structures \& Algorithms, Software Design
  }}
\end{itemize}

%--- Certifications ---
\section{Certifications}
\resumeSubHeadingListStart
  \resumeItem{AWS Certified Cloud Practitioner}
  \resumeItem{AWS Solutions Architect -- Associate}
  \resumeItem{Google Cloud Associate Cloud Engineer}
\resumeSubHeadingListEnd

\end{document}
