\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\input{glyphtounicode}
\pagestyle{fancy}\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}\addtolength{\textheight}{1.0in}
\urlstyle{same}\raggedbottom\raggedright\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\titlerule\vspace{-5pt}]
\pdfgentounicode=1

%--- Custom Commands ---
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[3]{\vspace{-2pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} & \textit{\small #3} \\
  \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={} ]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%--- Heading ---
\begin{center}
  \textbf{\Huge \scshape Yash Agarwal}\\
  \small
  +91-90276-01476 \textbar\ \href{mailto:190e785@gmail.com}{190e785@gmail.com} \\
  \href{https://in.linkedin.com/in/yash-agarwal-190e785}{LinkedIn} \textbar\ 
  \href{https://github.com/190-785}{GitHub}
\end{center}

%--- Education ---
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Graphic Era Hill University}{Dehradun, India}
    {B.Tech. in Computer Science \& Engineering, Honors in ML \& AI}{Aug 2023 -- Present}
\resumeSubHeadingListEnd

%--- Projects ---
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading{https://github.com/190-785/Plant_Watering_System}{IoT System with Dual Cloud Backends (Cloud \& IoT)}{June 2025 – July 2025}
    \resumeItemListStart
        \resumeItem{Engineered an automated plant watering system using an ESP8266 microcontroller that logs data to the cloud.}
        \resumeItem{Implemented two distinct backend versions using Firebase Firestore and Google Apps Script to compare performance.}
        \resumeItem{Logged and successfully stored over 10,000 unique data points from the sensor during a 30-day test period.}
    \resumeItemListEnd

    \resumeProjectHeading{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Platform (Full Stack)}{Feb 2025 – May 2025}
    \resumeItemListStart
        \resumeItem{Developed a full-stack application enabling users to create and manage resumes via an immersive 3D web interface.}
        \resumeItem{Built with a React/JavaScript frontend and a secure Node.js/Express backend using JWT for authentication.}
        \resumeItem{The platform successfully supports real-time editing and is designed to handle over 100 concurrent user sessions.}
    \resumeItemListEnd
    
    \resumeProjectHeading{https://github.com/190-785/First_Link_Backend}{Scalable Web Crawler API (Backend)}{October 2024 – November 2024}
    \resumeItemListStart
        \resumeItem{Architected a REST API in Python to trace the "first link" path on Wikipedia, handling complex traversal logic.}
        \resumeItem{Utilized a tech stack of Flask, Docker, MongoDB for storage, and Redis for caching to build a robust backend service.}
        \resumeItem{The implementation of Redis caching decreased average API response latency by over 60\% under repeated query loads.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--- Technical Profile ---
\section{Technical Profile}
\resumeSubHeadingListStart
    \item{\small
        \textbf{Technical Skills:} \\
        \begin{itemize}
            \item \textbf{Languages:} Python, Go (Foundational), Java, JavaScript, TypeScript
            \item \textbf{Backend:} Node.js, Express, REST APIs, Distributed Systems Concepts
            \item \textbf{Frameworks:} Flask, React, Vue.js, Tailwind CSS
            \item \textbf{Databases \& Caching:} MongoDB, PostgreSQL, Firebase Firestore, Redis
            \item \textbf{DevOps \& Cloud:} AWS, Docker, Git, CI/CD Practices, Linux/Unix Environments
        \end{itemize}
        \vspace{0.1cm}
        \textbf{Soft Skills:} Problem-Solving, Collaborative Development, Adaptability, Eager to Learn
    }
\resumeSubHeadingListEnd

%--- Cloud & Platform Proficiencies ---
\section{Cloud \& Platform Proficiencies}
\resumeSubHeadingListStart
    \resumeItem{AWS Certified Solutions Architect – Associate}
    \resumeItem{Google Cloud Associate Cloud Engineer}
\resumeSubHeadingListEnd

%--- Academic Subjects ---
\section{Academic Subjects}
\resumeSubHeadingListStart
    \item{\small Data Structures \& Algorithms, Object-Oriented Programming, Database Management Systems, Operating Systems}
\resumeSubHeadingListEnd

\end{document}
