%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{LinkedIn}} $|$
    \href{https://github.com/190-785}{\underline{GitHub}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Aug 2023 -- Present}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {Arterns Technologies Private Limited}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Developed and polished user-facing features for an Applicant Tracking System on \href{https://menticate.com}{\textbf{menticate.com}} using Next.js, significantly improving UI performance and workflow efficiency.}
        \resumeItem{Seamlessly integrated a real-time chat API, ensuring smooth, high-performance data flows between the frontend and backend services to enhance user interaction.}
        \resumeItem{Led the internationalization of \href{https://vedichealings.com}{\textbf{vedichealings.com}} by implementing the i18next library, launching full Spanish language support and improving accessibility for a global audience.}
        \resumeItem{Contributed to an Agile team by shipping meaningful bug fixes and improving feature reliability, which helped reduce project timeline overruns by 20\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, TypeScript, Spring Boot, MongoDB, WebSockets}
        \resumeItem{Architected a 0→1 product experiment to visualize resume data in an immersive 3D forest, creating an intelligent, user-friendly interface that redefines personal branding.}
        \resumeItem{Engineered a robust backend with secure JWT authentication and real-time collaboration features using WebSockets, allowing multiple users to edit seamlessly.}
        \resumeItem{\textbf{Outcome:} Delivered a novel, high-performance resume experience that increased user engagement and demonstrated innovative use of data visualization libraries.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, Redis, MongoDB, Docker, BeautifulSoup}
        \resumeItem{Developed a backend service to solve the "Philosophy Game" by tracing the traversal path from any Wikipedia page to 'Philosophy', handling complex loop and dead-end detection.}
        \resumeItem{Integrated Redis for caching common paths and containerized the application with Docker, ensuring scalability and faster response times under load.}
        \resumeItem{\textbf{Outcome:} Optimized pathfinding and parsing runtime by over 80\%, significantly improving performance and demonstrating strong analytical and problem-solving skills.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} ESP8266, Firebase, C++, ESPAsyncWebServer}
        \resumeItem{Designed an autonomous system to monitor soil moisture and dispense water, fully integrated with a cloud backend for remote management.}
        \resumeItem{Developed a secure web portal for Wi-Fi configuration and built a real-time dashboard using Firebase to monitor sensor data, providing a seamless remote user experience.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Python, Java, C++} \\
     \textbf{Frontend}{: React, Next.js, Three.js, HTML5, CSS3, Data Visualization} \\
     \textbf{Backend}{: Node.js, Spring Boot, Flask, REST/GraphQL APIs} \\
     \textbf{Databases \& Storage}{: MongoDB, Firebase, Redis} \\
     \textbf{Developer Tools}{: Git, Docker, Postman, WebSockets, GitHub Copilot, ChatGPT-4}
    }}
 \end{itemize}

%---------- Soft Skills ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Agile Collaboration, Proactive Problem-Solving, Cross-Functional Communication, Project Ownership, Teamwork \& Leadership}}
 \end{itemize}

\end{document}