%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
% Curated for Atlan AI Engineering Intern Role
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://linkedin.com/in/yash-agarwal-190e785}{\underline{LinkedIn}} $|$
    \href{https://github.com/190-785}{\underline{GitHub}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Aug 2023 -- Present}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {Arterns Technologies Private Limited}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Engineered a full-stack Applicant Tracking System (ATS) and student assessment module, focusing on efficient data management and retrieval for \href{https://menticate.com}{\textbf{menticate.com}}.}
        \resumeItem{Designed and integrated a real-time chat API, improving user interaction and data flow within the platform.}
        \resumeItem{Implemented internationalization (i18n) for \href{https://vedichealings.com}{\textbf{vedichealings.com}}, demonstrating attention to detail and ability to scale applications for diverse user bases.}
        \resumeItem{Operated within an Agile framework, contributing to a 20\% reduction in project timeline overruns by proactively identifying and mitigating development risks.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Graph-Based Pathfinding \& Optimization Engine}}}{Oct 2024 -- Dec 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Tech Stack:} Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}
            \resumeItem{Developed a backend service to solve the "Philosophy Game" by modeling Wikipedia as a graph and implementing a recursive traversal algorithm to find paths between nodes.}
            \resumeItem{Engineered a robust loop and dead-end detection system to handle complex edge cases in the data graph, ensuring reliable path discovery.}
            \resumeItem{\textbf{Outcome:} Optimized pathfinding runtime by over 80\% by integrating a Redis caching layer for frequently accessed paths, demonstrating a strong grasp of performance and scalability.}
          \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive Data Visualization \& Collaboration Platform}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, Spring Boot, MongoDB, WebSockets, JWT}
        \resumeItem{Architected a full-stack application to transform structured resume data into an immersive 3D environment, prototyping a novel method for user-data interaction.}
        \resumeItem{Built a real-time collaborative editing feature using WebSockets, allowing multiple users to interact and modify the underlying data model simultaneously.}
        \resumeItem{\textbf{Outcome:} Delivered a unique, proof-of-concept platform for personalized data representation, showcasing an experimental mindset and strong software engineering skills.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{Real-Time Sensor Data Pipeline \& IoT System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} C++, ESP8266, Firebase, ESPAsyncWebServer}
        \resumeItem{Designed and built an autonomous system to monitor and act on environmental data, demonstrating skills in rapid prototyping and hardware-software integration.}
        \resumeItem{Implemented a cloud-based data ingestion pipeline, logging real-time sensor telemetry to Firebase for remote monitoring and analysis.}
        \resumeItem{\textbf{Outcome:} Created a fully functional proof-of-concept that improved resource efficiency, showcasing the ability to build end-to-end data-driven systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript/TypeScript, C++} \\
     \textbf{AI/ML}{: Scikit-learn, TensorFlow, Keras, Prompt Engineering. \textit{Familiar with RAG Architectures, LangChain, LLM APIs.}} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Flask, Spring Boot} \\
     \textbf{Databases \& Data Stores}{: MongoDB, Firebase, Redis} \\
     \textbf{Developer Tools}{: Git, Docker, Postman, BeautifulSoup, Agile Methodologies}
    }}
 \end{itemize}

\end{document}