%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://linkedin.com/in/yash-agarwal-190e785}{\underline{LinkedIn}} $|$
    \href{https://github.com/190-785}{\underline{GitHub}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Aug 2023 -- Present}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Engineered a scalable full-stack Applicant Tracking System (ATS) and student assessment module for \href{https://menticate.com}{\textbf{menticate.com}}, improving data processing efficiency.}
        \resumeItem{Leveraged AI-powered tools like GitHub Copilot for code generation and debugging, accelerating development cycles and enhancing code quality.}
        \resumeItem{Developed and integrated backend services for a real-time chat API and implemented a site-wide dark theme, boosting user engagement.}
        \resumeItem{Implemented the i18next library in the \href{https://vedichealings.com}{\textbf{vedichealings.com}} Next.js codebase, launching full Spanish language support to expand market reach.}
        \resumeItem{Reduced project timeline overruns by 20\% by proactively identifying risks and implementing mitigation strategies within an Agile development environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, Redis, MongoDB, Docker, BeautifulSoup}
        \resumeItem{Developed a high-performance backend service to trace the traversal path from any Wikipedia page to the 'Philosophy' page, handling cycles and dead-ends efficiently.}
        \resumeItem{Integrated Redis for caching frequent paths, reducing average response times by over 80\% and significantly lowering database load.}
        \resumeItem{\textbf{Outcome:} Containerized the application with Docker for seamless deployment and scalability, optimizing pathfinding runtime and improving overall system resilience.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Java, Spring Boot, React, Three.js, MongoDB, WebSockets}
        \resumeItem{Architected a full-stack application with a Java-based Spring Boot backend to visualize resume data in an immersive 3D environment.}
        \resumeItem{Implemented secure, stateless JWT authentication and utilized WebSockets to enable real-time collaborative editing for a seamless multi-user experience.}
        \resumeItem{\textbf{Outcome:} Delivered a novel and highly interactive resume experience, demonstrating proficiency in building complex, stateful web applications.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} C++, ESP8266, Firebase, ESPAsyncWebServer}
        \resumeItem{Engineered an autonomous IoT system to stream real-time soil moisture telemetry to a Firebase cloud backend, triggering automated watering cycles.}
        \resumeItem{Developed a secure web portal for initial Wi-Fi configuration and implemented token-based authentication for remote management and data logging.}
        \resumeItem{\textbf{Outcome:} Improved water conservation and plant health, achieving a 20\% increase in watering efficiency and creating a scalable data pipeline for sensor data.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++} \\
     \textbf{Backend Frameworks}{: Spring Boot, Flask, Node.js} \\
     \textbf{Frontend Frameworks}{: React, Next.js} \\
     \textbf{Databases \& Storage}{: MongoDB, Firebase, Redis} \\
     \textbf{Developer Tools \& Platforms}{: Git, Docker, Postman, GitHub Copilot, BeautifulSoup} \\
     \textbf{Machine Learning}{: TensorFlow, Keras, scikit-learn, Matplotlib}
    }}
 \end{itemize}

\end{document}