%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based on: https://github.com/sb2nov/resume
% License : MIT
% Modified: AlgoUniversity Margins + Jake Styling
%------------------------

\documentclass[letterpaper,11pt]{article}
\setlength{\footskip}{4.08003pt}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-------------------------------------------
% 1-> ALGOUNIVERSITY MARGINS APPLIED HERE
% These values make the text area significantly wider and taller
%-------------------------------------------
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting (2-> Jake's Styling: Black, Standard Weight)
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands (3-> Jake's Alignment: 0.97 width, 0.15in margin)
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

% --- NEW COMMAND FOR PROJECT WITH GUIDE NAME ---
\newcommand{\resumeProjectHeadingGuide}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \small{Supervisor: \textit{#3}} & \\
    \end{tabular*}\vspace{-7pt}
}
% -----------------------------------------------

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\fontsize{26}{32}\selectfont \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91 9027601476 $|$ \href{mailto:yashagarwal1769@gmail.com}{\underline{yashagarwal1769@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/yash-agarwal-dev/}{\underline{linkedin.com/in/yash-agarwal-dev}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%-----------EDUCATION-----------
\section{Academic Details}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Dehradun, Uttarakhand}
      {Bachelor of Technology in Computer Science \& Engineering}{Aug 2023 -- Present}
    \resumeSubheading
      {St. Mary's School}{Kashipur, Uttarakhand}
      {Intermediate, CBSE}{2023}
    \resumeSubheading
      {St. Mary's School}{Kashipur, Uttarakhand}
      {High School, CBSE}{2021}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeadingGuide
          {\href{https://github.com/190-785/Interactive-Resume-Maker}{\textbf{Interactive Resume Maker}} $|$ \emph{Spring Boot, React, Three.js, MongoDB}}{Feb 2025 -- May 2025}
          {Prof. (Dr.) Prateek Shrivastava}
          \resumeItemListStart
            \resumeItem{Developed an immersive application to visualise user resumes in a 3D forest environment using Three.js.}
            \resumeItem{Created a secure backend using Spring Boot and Java 17, implementing JSON Web Tokens (JWT) \& BCrypt for authentication.}
            \resumeItem{Engineered RESTful APIs to manage user sessions and fetch resume data from MongoDB, enabling efficient data retrieval.}
          \resumeItemListEnd
          
      \resumeProjectHeadingGuide
          {\href{https://github.com/190-785/youtube-language-drift}{\textbf{YouTube Language Drift}} $|$ \emph{Python, NLTK, Scikit-Learn, YouTube API}}{Jan 2026 -- Present}
          {Prof. (Dr.) Susheela Dhaiya}
          \resumeItemListStart
            \resumeItem{Engineered a Natural Language Processing (NLP) pipeline to analyse linguistic evolution over the years, sampling 50 videos/year/creator to normalise bias across transcripts. }
            \resumeItem{Measured vocabulary shifts by calculating the Type-Token Ratio for lexical analysis and measuring year-over-year deviations.}
            \resumeItem{Analysed linguistic patterns using N-gram extraction and Jaccard similarity indices to identify trends using Matplotlib visualisation.}
            \resumeItem{Designed a reproducible workflow with structured configurations and randomised selection to ensure consistent experimental results across multiple execution runs.}
          \resumeItemListEnd
        
      \resumeProjectHeadingGuide
          {\href{https://github.com/190-785/final-year-portal}{\textbf{Final Year Project Management Portal}} $|$ \emph{Next.js, Firebase, Tailwind CSS v4}}{Aug 2025 -- Feb 2026}
          {Dr. Amit Gupta}
          \resumeItemListStart
            \resumeItem{Built a project management system using Next.js and Tailwind CSS for streamlining the workflow of students, faculty, external evaluators, and admin.}
            \resumeItem{Designed a Role-Based Access Control system using Firebase Authentication, implementing read/write permissions using Firestore rules. }
            \resumeItem{Implemented real-time data synchronisation using Firestore Listeners for instant updates for project submissions and faculty reviews.}
            \resumeItem{Structured a NoSQL (Firestore) database for complex relationships between users, teams, panellists, and external evaluators.}
          \resumeItemListEnd
          
      \resumeProjectHeadingGuide
          {\href{https://github.com/190-785/Plant_Watering_System}{\textbf{Smart Plant Watering System}} $|$ \emph{C++, Next.js, Firebase, IoT}}{June 2025 -- Aug 2025}
          {Dr. Vikrant Sharma}
          \resumeItemListStart
            \resumeItem{Developed an automated IoT system using ESP8266 to monitor and control soil moisture in real time.}
            \resumeItem{Built a web app using Next.js and Tailwind CSS for real-time data visualisation and remote control of the system.}
            \resumeItem{Created a secure architecture using MAC-based device identification, where hardware synchronises state changes directly from Firestore to eliminate vulnerable inbound HTTP endpoints.}
            \resumeItem{Implemented a captive portal for dynamic WiFi connection, enabling seamless device setup without the need for hardcoded credentials.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, C++, Python, JavaScript (ES6+), SQL, HTML/CSS} \\
     \textbf{Frameworks/Libraries}{: Spring Boot, React.js, Next.js, Three.js, Tailwind CSS v4, Flask, NLTK, Scikit-Learn} \\
     \textbf{Databases}{: MongoDB, Firebase (Firestore, Realtime DB), MySQL} \\
     \textbf{Tools}{: Git, Docker, Postman, Linux/Bash, Vercel, Arduino IDE} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}