%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal (Curated by Gemini for SWE Internship)
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{LinkedIn}} $|$
    \href{https://github.com/190-785}{\underline{GitHub}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Expected Aug 2027}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{July 2024 -- Dec 2024}
      {Arterns Technologies Private Limited}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Engineered and developed a full-stack Applicant Tracking System (ATS) and student assessment module for \href{https://menticate.com}{\textbf{menticate.com}}, improving operational efficiency.}
        \resumeItem{Enhanced user experience and engagement by integrating a real-time chat API and implementing a site-wide dark theme, demonstrating an interest in UI/UX design.}
        \resumeItem{Accelerated global accessibility for \href{https://vedichealings.com}{\textbf{vedichealings.com}} by implementing the i18next library, successfully launching full Spanish language support.}
        \resumeItem{Reduced project timeline overruns by 20\% by proactively identifying risks and implementing mitigation strategies in a collaborative Agile team environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, MongoDB, Spring Boot (Java), WebSockets, JWT}
        \resumeItem{Architected a scalable, full-stack application leveraging object-oriented design principles in Spring Boot to visualize resume data in an immersive 3D environment.}
        \resumeItem{Implemented secure, real-time collaboration features using WebSockets and JWT authentication, showcasing strong troubleshooting and debugging skills to ensure seamless multi-user editing.}
        \resumeItem{\textbf{Outcome:} Delivered an innovative user interface and experience, providing a novel alternative to traditional formats and demonstrating creative problem-solving.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}
        \resumeItem{Developed a performance-oriented backend service to trace traversal paths on Wikipedia, implementing robust logic to handle loops and dead-ends during network data retrieval.}
        \resumeItem{Designed a scalable architecture using Docker for containerization and integrated Redis caching to minimize latency and optimize performance for frequent requests.}
        \resumeItem{\textbf{Outcome:} Achieved an 80\% reduction in pathfinding runtime, significantly lowering server load and demonstrating strong programming skills inclined towards optimization.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} ESP8266, Firebase, ESPAsyncWebServer, C++}
        \resumeItem{Designed and developed an autonomous embedded system to monitor and control hardware, showcasing fundamentals of system-level programming and device interaction.}
        \resumeItem{Engineered a secure web portal for Wi-Fi configuration and logged real-time telemetry data to a cloud backend (Firebase) using token-based authentication (HTTPS).}
        \resumeItem{\textbf{Outcome:} Increased watering efficiency by 20\%, demonstrating skills in building reliable systems that integrate hardware, software, and cloud platforms.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Core Competencies \& Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Python, Java, C++, JavaScript, TypeScript} \\
      \textbf{CS Fundamentals}{: Data Structures, Algorithms, Object-Oriented Design (OOD), Operating Systems Concepts} \\
      \textbf{Networking Concepts}{: TCP/IP Fundamentals, HTTP/HTTPS, REST APIs} \\
      \textbf{Frameworks \& Libraries}{: React, Next.js, Node.js, Flask, Spring Boot, TensorFlow, Keras} \\
      \textbf{Databases \& Platforms}{: MongoDB, Firebase, Redis, Git, Docker, Postman}
    }}
 \end{itemize}

%---------- SOFT SKILLS ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Creative Problem-solving, Agile Collaboration, Troubleshooting \& Debugging, Teamwork, Communication}}
 \end{itemize}

\end{document}