%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{\textit{\small Aug 2023 -- Present}}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Engineered a data-driven Applicant Tracking System (ATS) and student assessment module for \href{https://menticate.com}{\textbf{menticate.com}}, managing complex user data flows.}
        \resumeItem{Developed and integrated multiple user-centric features, including a real-time chat API and a site-wide dark theme to enhance user experience.}
        \resumeItem{Refactored the \href{https://vedichealings.com}{\textbf{vedichealings.com}} codebase by implementing the i18next library, successfully launching full Spanish language support.}
        \resumeItem{Reduced project timeline overruns by 20\% by proactively identifying risks and implementing mitigation strategies in a fast-paced Agile environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Data Traversal and Caching System}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}
        \resumeItem{Developed a backend service to analyze and map complex data pathways from a given starting point within the Wikipedia dataset, implementing algorithms for loop and dead-end detection.}
        \resumeItem{Integrated Redis caching to store frequently accessed paths and utilized MongoDB for persistent storage, enhancing system performance and scalability.}
        \resumeItem{\textbf{Outcome:} Achieved an 80\% optimization in data processing and pathfinding runtime, significantly improving efficiency and reducing computational overhead.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Data Visualization Platform}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, MongoDB, Spring Boot, WebSockets}
        \resumeItem{Architected a full-stack application to transform structured user data into an immersive 3D environment, creating a novel data visualization interface.}
        \resumeItem{Implemented secure JWT authentication for data protection and utilized WebSockets to enable real-time multi-user collaboration and data synchronization.}
        \resumeItem{\textbf{Outcome:} Delivered a highly interactive platform that increased user engagement by presenting complex data in an intuitive, personalized visual format.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT-Based Telemetry and Automation System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} ESP8266, Firebase, ESPAsyncWebServer, C++}
        \resumeItem{Designed and built an autonomous system to collect and log real-time telemetry data (e.g., soil moisture) to a Firebase cloud backend for remote analysis and management.}
        \resumeItem{Developed a secure web portal for system configuration and authenticated real-time data logging to Firebase, ensuring data integrity.}
        \resumeItem{\textbf{Outcome:} Improved resource conservation by achieving a 20\% increase in watering efficiency through data-driven automation and remote monitoring.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++} \\
     \textbf{Data \& Analysis}{: Python (Pandas, NumPy), scikit-learn, Matplotlib, TensorFlow, Microsoft Excel (Advanced)} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Flask, Spring Boot} \\
     \textbf{Databases \& Storage}{: MongoDB, Firebase, Redis} \\
     \textbf{Developer Tools}{: Git, Docker, BeautifulSoup, Postman}
    }}
 \end{itemize}

%---------- SOFT SKILLS ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Agile Collaboration, Analytical Problem-Solving, Communication, High Attention to Detail, Teamwork, Adaptability}}
 \end{itemize}

\end{document}