%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://linkedin.com/in/yash-agarwal-190e785}{\underline{LinkedIn}} $|$
    \href{https://github.com/190-785}{\underline{GitHub}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Aug 2023 -- May 2026 (Expected)}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {Arterns Technologies Private Limited}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Developed a full-stack web application featuring an Applicant Tracking System (ATS) to solve business needs for candidate management and student assessment.}
        \resumeItem{Integrated third-party APIs for real-time chat functionality, improving user engagement and providing a more dynamic, interactive platform for clients.}
        \resumeItem{Engineered a scalable front-end by implementing internationalization (i18next), enabling the platform to support a global user base with an initial launch in Spanish.}
        \resumeItem{Owned key feature development within an Agile framework, contributing to a 20\% reduction in project overruns by identifying and mitigating technical risks.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Scalable Web Service for Pathfinding}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, Redis, MongoDB, Docker, BeautifulSoup}
        \resumeItem{Architected a resilient backend service to process and trace paths through Wikipedia's large dataset, implementing algorithms to handle complex traversal logic and loop detection.}
        \resumeItem{Engineered a high-performance, scalable platform by integrating Redis for caching to reduce latency and leveraging Docker for containerized deployment, improving system resiliency.}
        \resumeItem{\textbf{Outcome:} Achieved an 80\% reduction in pathfinding runtime for cached results, demonstrating significant improvements in efficiency for data-intensive operations.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Customized 3D Resume Web Application}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Java, Spring Boot, React, Three.js, MongoDB, WebSockets}
        \resumeItem{Designed and developed a proof-of-concept web application to provide a customized solution for data visualization, transforming standard resume data into an interactive 3D environment.}
        \resumeItem{Built a secure, collaborative platform using a Spring Boot backend with JWT authentication and a React front-end leveraging WebSockets for real-time, multi-user editing.}
        \resumeItem{\textbf{Outcome:} Created a novel and engaging user experience, demonstrating the ability to build bespoke, full-stack solutions to address unique client-style business challenges.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Solution with Web-Based Management}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} C++, ESP8266, Firebase, JavaScript}
        \resumeItem{Developed a full-stack IoT solution integrating a C++ based microcontroller with a cloud backend (Firebase) for real-time data synchronization and remote management.}
        \resumeItem{Built a secure, web-based portal for device configuration and data monitoring, demonstrating end-to-end ownership of the solution lifecycle from hardware to a client-facing interface.}
        \resumeItem{\textbf{Outcome:} Delivered an efficient, automated system with a modular design, improving water conservation by 20\% and showcasing skills in building integrated solutions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C++, JavaScript, TypeScript} \\
     \textbf{Frameworks}{: Spring Boot, React, Next.js, Node.js, Flask} \\
     \textbf{Databases \& Storage}{: MongoDB, Redis, Firebase} \\
     \textbf{Developer Tools}{: Git, Docker, REST APIs, Postman, BeautifulSoup} \\
     \textbf{Machine Learning}{: TensorFlow, Keras, scikit-learn, Matplotlib}
    }}
 \end{itemize}

%---------- SOFT SKILLS ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Technical Consulting, Cross-functional Collaboration, Problem-Solving, Solution Ownership}}
 \end{itemize}

\end{document}