%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Targeted for: iRage (HFT/Quant)
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91 9027601476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Aug 2023 -- July 2027}
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
% Moved up for HFT relevance
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, Java, JavaScript, TypeScript, SQL} \\
     \textbf{Core Concepts}{: Data Structures \& Algorithms, OOPS, DBMS, Operating Systems, System Design} \\
     \textbf{Technologies}{: Node.js, React, Redis, Firebase, Docker, MongoDB, Socket.io, Git} \\
     \textbf{Libraries}{: STL (C++), NumPy, Pandas, Scikit-learn, BeautifulSoup}
    }}
 \end{itemize}

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://drive.google.com/file/d/1OzMx9okAmp5j0GACBHkKpYvhwXmD1Dwg/view?usp=drive_link}{DataCulture Technologies Private Limited}}{New Delhi, India (Hybrid)}
      {IoT \& Software Developer Intern}{May 2025 -- Nov 2025}
      \resumeItemListStart
        \resumeItem{Engineered firmware using \textbf{C++} for an automated irrigation system, optimizing sensor polling intervals to reduce power consumption while maintaining real-time data accuracy.}
        \resumeItem{Developed a low-latency telemetry dashboard using React and Firebase, handling real-time state synchronization for remote hardware control and monitoring.}
        \resumeItem{\textbf{Patent Filed:} Co-authored and filed a patent for the system's novel architectural approach to remote agricultural automation and water conservation.}
        \resumeItem{\textbf{Performance:} Achieved "Exceeded Expectations" rating in Technical Competency and Deliverables. Commended for strong documentation practices and collaborative problem-solving.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      {Full-Stack Web Developer Intern}{May 2025 -- July 2025}
      \resumeItemListStart
        \resumeItem{Architected a scalable Applicant Tracking System (ATS) backend using Node.js; optimized API response times for parsing large volumes of resume data.}
        \resumeItem{Implemented real-time bi-directional communication using \textbf{Socket.io}, enabling instant messaging and live status updates with minimal latency.}
        \resumeItem{Refactored legacy codebases to support i18next internationalization, improving maintainability and extending platform reach to Spanish-speaking demographics.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
   
    % PROJECT 1: Best for HFT (Algorithms, Optimization, Caching)
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Distributed Path Finder}} $|$ \textit{Python, Redis, Docker, Algorithms}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{Designed a graph traversal engine to trace paths between Wikipedia pages; implemented \textbf{intelligent loop detection} and dead-end handling algorithms to ensure traversal validity.}
        \resumeItem{Engineered a two-tier caching layer using \textbf{Redis}, reducing redundant network requests and cutting average pathfinding runtime by \textbf{80\%}.}
        \resumeItem{Containerized the application using Docker for consistent deployment and horizontal scalability across distributed environments.}
      \resumeItemListEnd

    % PROJECT 2: Best for Concurrency/Data Handling
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Daily_Ledger}{Daily Ledger - Real-Time Transaction System}} $|$ \textit{React, Firebase, Logic}}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built a high-concurrency transaction tracking system supporting real-time collaborative editing. Implemented optimistic UI updates to mask network latency for a seamless user experience.}
        \resumeItem{Designed a robust Firestore schema with granular security rules (Row Level Security equivalent) to handle multi-user permissions and secure concurrent writes.}
        \resumeItem{Optimized bundle size to 208 KB (gzipped) achieving 90+ Lighthouse performance scores.}
      \resumeItemListEnd
   
    % PROJECT 3: Best for Scale
    \resumeProjectHeading
      {\textbf{\href{https://final-year-portal.vercel.app}{University Project Management Portal}} $|$ \textit{Next.js, Node.js, System Design}}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Architected a system supporting \textbf{1,500+ concurrent users} with role-based access control for students, faculty, and external auditors.}
        \resumeItem{Modeled complex relationships for 400+ project teams, optimizing database queries to handle heavy read/write loads during submission deadlines.}
        \resumeItem{Deployed production-ready infrastructure scheduled for campus-wide adoption in 2026.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

\end{document}