%-------------------------
% Resume in Latex
% Author : Yash Agarwal
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91 9027601476 $|$ \href{mailto:yashagarwal1769@gmail.com}{\underline{yashagarwal1769@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Aug 2023 -- July 2027}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full-Stack / Product Engineer}{Aug 2025 -- Present}
      {Graphic Era Hill University (Campus Deployment)}{Dehradun, India}
      \resumeItemListStart
        \resumeItem{Led the system architecture and operational deployment of a production portal engineered for high availability and horizontal scaling to support 1,600+ users with planned scale to 4,000 users; focused on stateless service patterns and efficient data partitioning.}
        \resumeItem{Architected Firestore data model with role-based access control, atomic transactions, composite indexes, and strict security rules; authored test suites using the Firestore emulator to validate rules and transactions.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://drive.google.com/file/d/1OzMx9okAmp5j0GACBHkKpYvhwXmD1Dwg/view}{Software Engineering Intern (IoT \& Full-Stack)}}{May 2025 -- Nov 2025}
      {DataCulture Technologies Pvt. Ltd.}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered an end-to-end IoT irrigation system spanning embedded C++ firmware, reliable cloud ingestion, and a Next.js dashboard; implemented token-based authentication and deterministic retry/backoff to ensure resilient telemetry ingestion.}
        \resumeItem{Designed REST and WebSocket APIs for live telemetry and control, implemented client-side buffering and idempotent ingestion to tolerate intermittent connectivity, and established CI checks and integration tests for core flows.}
        \resumeItem{Defined deterministic, state-driven control logic for hardware fault handling and safety interlocks; co-authored a patent application for the system architecture and remote control methodology.}
      \resumeItemListEnd

    \resumeSubheading
     {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view}{Full Stack Developer Intern (Part-Time)}}{May 2025 -- July 2025}
      {Arterns Technologies Pvt. Ltd.}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered production frontends with performance and accessibility in mind using Next.js and Tailwind; implemented server-side rendering and client hydration strategies to improve perceived load times.}
        \resumeItem{Built a horizontally scalable real-time chat system using Socket.io and Firebase, with message ordering, reconnection handling, and backpressure controls to maintain correctness under load.}
        \resumeItem{Managed end-to-end delivery including automated deployments on Vercel, lightweight backend integrations, and consistent authentication flows verified through integration tests.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Portfolio}} $|$ \emph{React, Three.js, Spring Boot, MongoDB}}{Feb 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Developed an immersive 3D experience using Three.js, optimizing scene graph design, GPU instancing, and texture atlasing to reduce draw calls and frame stalls.}
            \resumeItem{Designed a Spring Boot REST API backend with JWT-secured CRUD operations and rate-limited endpoints; structured APIs for predictable latency under client load.}
            \resumeItem{Optimized asset orchestration, lazy loading, and startup sequencing to improve initial render times and overall runtime performance.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{https://github.com/190-785/Daily-Ledger}{Real-time Community Finance Tracker}} $|$ \emph{React PWA, Firestore, Tailwind}}{Oct 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Built an offline-first Progressive Web App using service workers and local persistence to ensure reliable writes while offline and correct sync on reconnect.}
            \resumeItem{Designed Firestore data model and security rules to enforce RBAC and ensure idempotent ledger entries; implemented transactions and optimistic concurrency control for consistent financial state.}
            \resumeItem{Implemented an in-browser SheetJS export engine and automated reporting tools to produce auditable monthly reports and to simplify reconciliations.}
          \resumeItemListEnd

      % \resumeProjectHeading
      %     {\textbf{\href{https://github.com/190-785/First-Link-Backend}{Wikipedia Philosophy Crawler}} $|$ \emph{Python, Selenium, Docker, Flask}}{Oct 2024 -- Dec 2024}
      %     \resumeItemListStart
      %       \resumeItem{Engineered a recursive web-crawling engine using Selenium WebDriver and XPath selectors to automate the Wikipedia ``Getting to Philosophy'' traversal rule.}
      %       \resumeItem{Optimized crawl latency by introducing memoized jump paths and loop detection algorithms, exposing results via a RESTful Flask API.}
      %       \resumeItem{Containerized the application with a headless Chrome runtime using Docker to ensure consistent execution and deterministic session management.}
      %     \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, Python, Java, C++, SQL} \\
     \textbf{Frontend}{: React, Next.js, Tailwind CSS, Three.js, Vite} \\
     \textbf{Backend \& Cloud}{: Node.js, Express, Spring Boot, Firebase (Auth/Firestore), MongoDB, Redis, Docker} \\
     \textbf{Tools}{: Git, GitHub Actions, Docker Compose, Selenium, PlatformIO, Postman}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
