%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\ % Changed this line
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{\textit{\small Aug 2023 -- Present}}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Developed a full-stack Applicant Tracking System (ATS) with automated resume parsing and student assessment module for \href{https://menticate.com}{\textbf{menticate.com}}, building Node.js backend APIs with Firebase authentication and database.}
        \resumeItem{Integrated Socket.io and Firebase for real-time chat functionality, and architected a reusable theme system enabling seamless site-wide dark mode across multiple pages and components.}
        \resumeItem{Led the development of \href{https://we-are-on-leaf.vercel.app}{\textbf{we-are-on-leaf.vercel.app}} and implemented i18next internationalization across 8+ pages in \href{https://vedichealings.com}{\textbf{vedichealings.com}} Next.js codebase, delivering complete Spanish language support.}
        \resumeItem{Reduced project timeline overruns by 20\% by identifying and resolving critical API authentication issues and implementing proactive risk mitigation strategies in an Agile environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://final-year-portal.vercel.app}{Final Year Project Management Portal}}}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Next.js, Firebase, Tailwind CSS, Node.js}
        \resumeItem{Architected and developed the backend infrastructure for a comprehensive project management system serving 1,500+ students, scaling to 3,000+ users across multiple campuses by 2026, managing 400+ project teams across multiple evaluation phases.}
        \resumeItem{Designed a multi-role access control system with distinct dashboards for students, administrators, faculty, panelists, and external reviewers, implementing secure Firebase authentication and real-time email notification workflows.}
        \resumeItem{\textbf{Outcome:} Deployed production-ready platform scheduled for official university-wide adoption, streamlining project evaluation workflows and enabling faculty to schedule meetings with automated team notifications.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, MongoDB, Spring Boot, WebSockets}
        \resumeItem{Architected a full-stack application to visualize resume data in an immersive 3D forest environment, offering a unique and engaging user interface.}
        \resumeItem{Implemented secure JWT authentication, auto-save versioning, and real-time collaboration features using WebSockets to allow for seamless multi-user editing.}
        \resumeItem{\textbf{Outcome:} Delivered a highly interactive and personalized resume experience, increasing user engagement and providing a novel alternative to traditional formats.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}
        \resumeItem{Developed a backend service to trace the traversal path from a given Wikipedia page to the 'Philosophy' page by recursively clicking the first link, detecting loops and dead-ends.}
        \resumeItem{Integrated Redis caching to store frequent paths and Docker for containerization, ensuring scalability and faster response times under load.}
        \resumeItem{\textbf{Outcome:} Optimized pathfinding and parsing runtime by approximately 80\%, significantly lowering infrastructure costs and improving user experience.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Flask, Spring Boot} \\
     \textbf{Databases \& Storage}{: MongoDB, Firebase, Redis} \\
     \textbf{Developer Tools}{: Git, Docker, Postman} \\
     \textbf{Machine Learning}{: scikit-learn, TensorFlow, Keras}
    }}
 \end{itemize}

\end{document}