%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{\textit{\small Aug 2023 -- Present}}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Designed and implemented a full-stack Applicant Tracking System (React, Node.js, MongoDB) to centralize candidate workflows and reduce manual candidate processing time for recruiters.}
        \resumeItem{Implemented a real-time chat feature using WebSockets and Node.js, enabling concurrent messaging and presence indicators; added server-side message persistence and monitoring to improve message reliability in production.}
        \resumeItem{Integrated i18next into a Next.js codebase for \href{https://vedichealings.com}{\textbf{vedichealings.com}}, adding runtime language switching and unit tests for localization strings to improve accessibility for Spanish-speaking users.}
        \resumeItem{Implemented pre-merge CI checks and standardized story sizing to improve sprint predictability, contributing to a 20\% reduction in delivery overruns.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} ESP8266, Firebase, ESPAsyncWebServer, C++}
        \resumeItem{Designed and implemented embedded firmware for ESP8266 to sample soil-moisture sensors and trigger actuators with debounce and fail-safe logic, preventing overwatering and ensuring safety.}
        \resumeItem{Implemented token-based authentication for Firebase telemetry ingestion and added reconnection and retry logic to handle intermittent Wi-Fi, improving telemetry reliability.}
        \resumeItem{Built a lightweight web portal for Wi-Fi provisioning and remote control; logged telemetry and actuator events to Firebase for historical analysis, increasing watering efficiency by 20\% during field trials.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, MongoDB, Spring Boot, WebSockets}
        \resumeItem{Designed and implemented a React and Three.js front end that renders resume data in an interactive 3D scene with level-of-detail culling to maintain frame rate under load.}
        \resumeItem{Implemented a Spring Boot API with JWT authentication and a versioned MongoDB schema; added optimistic locking and end-to-end tests to prevent concurrent edit conflicts.}
        \resumeItem{Implemented auto-save and real-time collaboration via WebSockets and added monitoring to observe edit events and sync latency, improving multi-user editing reliability.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}
        \resumeItem{Designed and implemented a Flask service that parses and follows the first-link chain on Wikipedia pages using a BFS-style traversal with loop detection and dead-end handling to avoid infinite recursion.}
        \resumeItem{Implemented Redis caching for computed paths and Dockerized the service for repeatable deployment; added integration tests and basic metrics to track cache hit rate.}
        \resumeItem{Optimized parsing and caching strategy to reduce average pathfinding runtime by approximately 80\%, lowering compute costs and improving user response times.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Flask, Spring Boot} \\
     \textbf{Databases \& Storage}{: MongoDB, Firebase, Redis} \\
     \textbf{Developer Tools}{: Git, Docker, Postman, BeautifulSoup} \\
     \textbf{Machine Learning}{: scikit-learn, TensorFlow, Keras, Matplotlib}
    }}
 \end{itemize}

%---------- SOFT SKILLS ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Problem-Solving, Time Management, Agile Collaboration, Communication, Teamwork}}
 \end{itemize}

\end{document}
