%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\ % Changed this line
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{\textit{\small Aug 2023 -- Present}}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{May 2025 -- July 2025}
      {Arterns Technologies Private Limited}{Dehradun, India}
      \resumeItemListStart
        \resumeItem{Developed scalable back-end APIs and server-side logic for an Applicant Tracking System handling high-volume requests.}
        \resumeItem{Implemented secure real-time features (chat, assessment pipelines) ensuring low-latency asynchronous communication.}
        \resumeItem{Optimized database queries and caching strategies, reducing API response times by 20\%.}
        \resumeItem{Worked in an Agile team, collaborating with designers, QA, and backend developers to deliver production-ready solutions using CI/CD pipelines.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, MongoDB, Redis, Docker}
        \resumeItem{Built a scalable service to compute paths between Wikipedia pages by recursively traversing first links, handling cycles and dead ends.}
        \resumeItem{Designed efficient caching strategies using Redis, achieving $\sim$80\% runtime improvement under high-volume queries.}
        \resumeItem{Containerized with Docker and optimized request handling for scalability in production-like environments.}
      \resumeItemListEnd
      
           \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{Built an autonomous IoT solution with ESP8266 and soil-moisture sensors for automated irrigation.}
        \resumeItem{Integrated Firebase with secure token-based authentication for real-time data logging.}
        \resumeItem{Developed an asynchronous web server for Wi-Fi configuration and remote control.}
        \resumeItem{Optimized firmware with interrupt-driven sensor handling to reduce latency and power usage.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Developed a 3D resume visualization tool using React, Three.js, and Spring Boot.}
        \resumeItem{Implemented JWT authentication and scalable MongoDB backend for secure data storage.}
        \resumeItem{Enabled real-time collaboration via WebSockets with auto-save and versioning.}
        \resumeItem{Optimized performance with asset lazy-loading and Docker-based CI/CD deployment.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Core CS}{: Data Structures, Algorithms, Operating Systems, DBMS, OOP} \\
     \textbf{Languages}{: Python, Java, C++, JavaScript, TypeScript} \\
     \textbf{Back-end \& Systems}{: Flask, Node.js, Spring Boot, REST APIs, Redis, Docker} \\
     \textbf{Machine Learning}{: TensorFlow, Keras, scikit-learn, Pandas, NumPy} \\
     \textbf{Databases}{: MongoDB, Firebase, SQL} \\
     \textbf{Developer Tools}{: Git, Azure DevOps, Postman, Linux}
    }}
 \end{itemize}

%---------- SOFT SKILLS ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Problem Solving, Scalability Thinking, Collaboration, Communication, Agile/Scrum}}
 \end{itemize}

 
\end{document}