%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small Full-Stack Software Engineer \\ \vspace{1pt}
    \small +91 9027601476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{\textit{\small Aug 2023 -- July 2027}}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Full-Stack Web Developer Intern}{May 2025 -- July 2025}
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Developed backend infrastructure for an Applicant Tracking System featuring automated resume parsing capabilities. Designed RESTful APIs and implemented Firebase database architecture with secure authentication using Node.js.}
        \resumeItem{Engineered real-time communication system using Socket.io integrated with Firebase, enabling efficient data synchronization across distributed clients with support for multiple concurrent connections.}
        \resumeItem{Led full-stack development of a corporate wellness platform, implementing internationalization across 8+ pages in Next.js while managing content delivery and locale-specific routing.}
        \resumeItem{Reduced deployment failures by 20\% through systematic debugging of API authentication workflows and implementation of comprehensive error handling mechanisms.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart
  
    \resumeProjectHeading
      {\textbf{\href{https://final-year-portal.vercel.app}{Final Year Project Management Portal}}}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Next.js, Firebase (Firestore, Authentication), Node.js, Tailwind CSS}
        \resumeItem{Architected scalable backend supporting 1,500+ concurrent users for university-wide final year project management system. Implemented complex data modeling for 400+ project teams with multi-phase workflow tracking and evaluation.}
        \resumeItem{Engineered role-based access control system with five permission levels ensuring secure data access. Integrated Firebase Authentication with custom claims and optimized database schemas for enhanced query performance.}
        \resumeItem{Deployed production system with automated email notifications and real-time synchronization, achieving sub-200ms API response times. Platform scaling to 3,000+ users across multiple campuses starting 2026.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}
        \resumeItem{Developed distributed backend service tracing Wikipedia page connections using breadth-first search algorithm with intelligent loop detection and dead-end handling mechanisms.}
        \resumeItem{Implemented two-tier caching strategy utilizing Redis for hot paths and MongoDB for persistent storage. Containerized application with Docker enabling horizontal scalability and efficient load distribution.}
        \resumeItem{Achieved 80\% reduction in average query latency and 65\% decrease in database load through optimization, enabling 10x increase in concurrent request capacity.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, MongoDB, Spring Boot, WebSockets}
        \resumeItem{Developed and maintained RESTful backend services using Spring Boot with MongoDB integration. Implemented JWT authentication, session management, and auto-save functionality with optimistic locking for concurrent editing.}
        \resumeItem{Architected WebSocket infrastructure enabling real-time collaboration with conflict resolution and operational transformation, supporting synchronized multi-user editing with sub-second latency.}
        \resumeItem{Delivered production-ready full-stack application supporting collaborative editing with automatic version control and rollback capabilities.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++, SQL} \\
     \textbf{Backend \& Frameworks}{: Spring Boot, Node.js, Flask, Express.js, RESTful APIs} \\
     \textbf{Frontend}{: React, Next.js, HTML5, CSS3, Tailwind CSS} \\
     \textbf{Databases}{: MongoDB, Firebase Firestore, Redis, MySQL} \\
     \textbf{DevOps \& Tools}{: Docker, Git, Firebase Cloud, Postman, WebSockets, Socket.io}
    }}
 \end{itemize}

\end{document}