%-------------------------
 % Resume in LaTeX
 % Author: Yash Agarwal
 % Template Based on: sb2nov/resume (MIT License)
 %------------------------

 \documentclass[letterpaper,11pt]{article}

 \usepackage{latexsym}
 \usepackage[empty]{fullpage}
 \usepackage{titlesec}
 \usepackage{marvosym}
 \usepackage[usenames,dvipsnames]{color}
 \usepackage{verbatim}
 \usepackage{enumitem}
 \usepackage[hidelinks]{hyperref}
 \usepackage{fancyhdr}
 \usepackage[english]{babel}
 \usepackage{tabularx}
 \input{glyphtounicode}

 %----- FORMATTING & MARGINS -----
 \pagestyle{fancy}
 \fancyhf{}
 \fancyfoot{}
 \renewcommand{\headrulewidth}{0pt}
 \renewcommand{\footrulewidth}{0pt}

 \addtolength{\oddsidemargin}{-0.5in}
 \addtolength{\evensidemargin}{-0.5in}
 \addtolength{\textwidth}{1in}
 \addtolength{\topmargin}{-.5in}
 \addtolength{\textheight}{1.0in}

 \urlstyle{same}
 \raggedbottom
 \raggedright
 \setlength{\tabcolsep}{0in}

 %----- SECTION FORMATTING -----
 \titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
 }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

 %----- ATS COMPATIBILITY -----
 \pdfgentounicode=1

 %----- CUSTOM COMMANDS -----
 \newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
 \newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{#1} & \textit{\small #2} \\
  \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
 }
 \newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \small#1 & \textit{\small #2}
  \end{tabular*}\vspace{-3pt}
 }
 \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
 \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
 \newcommand{\resumeItemListStart}{\begin{itemize}}
 \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

 %-------------------------------------------
 %%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
 %-------------------------------------------

 \begin{document}

 %---------- HEADING ----------
 \begin{center}
  \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
  \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
  \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
  \href{https://github.com/190-785}{\underline{github.com/190-785}}
 \end{center}

 %---------- EDUCATION ----------
 \section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Graphic Era Hill University}{Uttarakhand, India}
  {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{Aug 2019 -- May 2023}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
{\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Engineered a full-stack Applicant Tracking System (ATS) and student assessment module for \href{https://menticate.com}{\textbf{menticate.com}}.}
        \resumeItem{Integrated a real-time chat API and implemented a site-wide dark theme to enhance the user experience.}
        \resumeItem{Implemented the i18next library in the \href{https://vedichealings.com}{\textbf{vedichealings.com}} Next.js codebase, launching full Spanish language support.}
        \resumeItem{Reduced project timeline overruns by 20\% by proactively identifying risks and implementing mitigation strategies in an Agile environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

 %---------- PROJECTS ----------
 \section{Projects}
  \resumeSubHeadingListStart
  \resumeProjectHeading
  {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}}}{Jun 2025 -- Jul 2025}
  \resumeItemListStart
  \resumeItem{\textbf{Tech Stack:} ESP8266, Firebase, ESPAsyncWebServer, C++}
  \resumeItem{Identified user needs for efficient home plant care and developed a product vision for an autonomous, cloud-managed watering system.}
  \resumeItem{Analyzed market trends in IoT home automation to design a scalable and secure solution with a web portal for remote configuration and data monitoring.}
  \resumeItem{\textbf{Outcome:} Delivered a product that improved water conservation and plant health, achieving a 20\% increase in watering efficiency.}
  \resumeItemListEnd
  
  \resumeProjectHeading
  {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
  \resumeItemListStart
  \resumeItem{\textbf{Tech Stack:} React, Three.js, MongoDB, Spring Boot, WebSockets}
  \resumeItem{Defined a product strategy to disrupt traditional resume formats by creating an immersive 3D visualization application to increase user engagement.}
  \resumeItem{Partnered with engineering to build a feature-rich platform including secure JWT authentication and real-time collaboration using WebSockets.}
  \resumeItem{\textbf{Outcome:} Shipped a novel product that provided a highly interactive and personalized resume experience, validated through positive user feedback.}
  \resumeItemListEnd
  
  \resumeProjectHeading
  {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
  \resumeItemListStart
  \resumeItem{\textbf{Tech Stack:} Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}
  \resumeItem{Analyzed performance bottlenecks in data parsing to design a backend service that traces Wikipedia link paths with loop and dead-end detection.}
  \resumeItem{Drove the technical strategy to integrate Redis caching and Docker containerization, ensuring product scalability and faster response times.}
  \resumeItem{\textbf{Outcome:} Successfully launched a service with an 80\% reduction in pathfinding runtime, significantly lowering infrastructure costs and improving user experience.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd

 %---------- TECHNICAL SKILLS ----------
 \section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
  \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++} \\
  \textbf{Frameworks}{: React, Next.js, Node.js, Flask, Spring Boot} \\
  \textbf{Databases \& Storage}{: MongoDB, Firebase, Redis} \\
  \textbf{Developer Tools}{: Git, Docker, Postman, Agile/Scrum} \\
  \textbf{Machine Learning}{: Matplotlib, scikit-learn, TensorFlow, Keras}
  }}
 \end{itemize}

 %---------- SOFT SKILLS ----------
 \section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{Agile Collaboration, Leadership, Stakeholder Management, Communication, Problem-solving}}
 \end{itemize}

 \end{document}