%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91 9027601476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{\textit{\small Aug 2023 -- July 2027}}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Full-Stack Web Developer Intern}{May 2025 -- July 2025}
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Developed full-stack Applicant Tracking System (ATS) with automated resume parsing and student assessment module for \href{https://menticate.com}{\textbf{menticate.com}}. Built Node.js backend APIs with Firebase authentication and database integration.}
        \resumeItem{Engineered real-time chat functionality using Socket.io integrated with Firebase, and architected reusable theme system enabling seamless site-wide dark mode across multiple pages and components.}
        \resumeItem{Led development of \href{https://we-are-on-leaf.vercel.app}{\textbf{we-are-on-leaf.vercel.app}} and implemented i18next internationalization across 8+ pages in \href{https://vedichealings.com}{\textbf{vedichealings.com}} Next.js codebase, delivering complete Spanish language support.}
        \resumeItem{Reduced project timeline overruns by 20\% by identifying and resolving critical API authentication issues, implementing proactive risk mitigation strategies in an Agile environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
%---------- INSTRUCTIONS: Uncomment/comment projects based on job requirements ----------
%---------- Keep 3-4 most relevant projects per application ----------
\section{Projects}
  \resumeSubHeadingListStart
  
    % PROJECT 1: Daily Ledger - Best for: Real-time collaboration, PWA, modern web stack, Firebase
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Daily_Ledger}{Daily Ledger - Smart Collection Tracker}} $|$ \textit{React, Firebase, Vite, Tailwind}}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built production-ready Progressive Web App (PWA) for real-time collection management with collaborative list sharing, offline support, and installable mobile experience. Deployed on Vercel with comprehensive Firebase security rules protecting user data and access control.}
        \resumeItem{Implemented real-time collaboration system enabling users to share collection lists with granular permissions and instant synchronization across devices. Architected Firestore data model with owner-based access control, member management, and transaction tracking supporting concurrent multi-user editing.}
        \resumeItem{\textbf{Outcome:} Achieved Lighthouse score of 90+ across all metrics with 208 KB gzipped bundle size. Engineered analytics dashboard with daily summaries, monthly targets, payment tracking, and Excel export functionality for data-driven decision making.}
      \resumeItemListEnd
  
    % PROJECT 2: Final Year Portal - Best for: Web platforms, full-stack, large-scale systems
    \resumeProjectHeading
      {\textbf{\href{https://final-year-portal.vercel.app}{Final Year Project Management Portal}} $|$ \textit{Next.js, Firebase, Node.js, Tailwind}}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Architected scalable backend infrastructure supporting 1,500+ concurrent users for university-wide final year project management system. Implemented complex data modeling for 400+ project teams with multi-phase workflow tracking and evaluation.}
        \resumeItem{Engineered multi-role access control system with distinct dashboards for students, administrators, faculty, panelists, and external reviewers. Integrated Firebase authentication with real-time email notification workflows.}
        \resumeItem{\textbf{Outcome:} Deployed production-ready platform scheduled for official university-wide adoption, streamlining project evaluation workflows and enabling automated meeting scheduling with team notifications. Platform scaling to 3,000+ users across multiple campuses starting 2026.}
      \resumeItemListEnd
      
    % PROJECT 3: 3D Resume Builder - Best for: Creative roles, frontend-heavy, real-time features
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}} $|$ \textit{React, Three.js, MongoDB, Spring Boot}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Developed full-stack application visualizing resume data in an immersive 3D forest environment, offering unique and engaging user interface experience.}
        \resumeItem{Implemented secure JWT authentication, auto-save versioning, and real-time collaboration features using WebSockets, enabling seamless multi-user editing with conflict resolution.}
        \resumeItem{\textbf{Outcome:} Delivered highly interactive and personalized resume experience, increasing user engagement and providing novel alternative to traditional formats.}
      \resumeItemListEnd
      
    % PROJECT 4: Wikipedia Path Finder - Best for: Algorithms, optimization, backend systems
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}} $|$ \textit{Python, Flask, BeautifulSoup, Redis, MongoDB, Docker}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{Developed distributed backend service tracing traversal path from given Wikipedia page to 'Philosophy' page by recursively clicking first link, implementing intelligent loop detection and dead-end handling.}
        \resumeItem{Implemented two-tier caching strategy utilizing Redis for frequent paths and Docker containerization, ensuring horizontal scalability and faster response times under load.}
        \resumeItem{\textbf{Outcome:} Achieved 80\% reduction in pathfinding and parsing runtime through optimization, significantly lowering infrastructure costs and improving user experience.}
      \resumeItemListEnd
      
    % PROJECT 5: IoT Plant Watering System - Best for: IoT roles, embedded systems, hardware integration
    % COMMENT OUT for most software engineering roles, UNCOMMENT for IoT/hardware positions
    % \resumeProjectHeading
    %   {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}} $|$ \textit{ESP8266, Firebase, React, C++}}{Jun 2025 -- Jul 2025}
    %   \resumeItemListStart
    %     \resumeItem{Designed and built autonomous IoT system monitoring soil moisture and dispensing water, fully integrated with cloud backend and real-time web dashboard at \href{https://bloomwatch-webapp.vercel.app}{\textbf{bloomwatch-webapp.vercel.app}} for remote monitoring and control.}
    %     \resumeItem{Engineered secure Wi-Fi configuration portal and implemented token-based Firebase authentication, enabling users to adjust moisture thresholds, watering cycles, and manually trigger pumps with safety features through interactive dashboard displaying real-time telemetry graphs.}
    %     \resumeItem{\textbf{Outcome:} Improved water conservation and plant health with 20\% increase in watering efficiency; preparing for commercial launch with modular hardware design for scalability.}
    %   \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Flask, Spring Boot} \\
     \textbf{Databases \& Storage}{: MongoDB, Firebase, Redis, PostgreSQL} \\
     \textbf{Developer Tools}{: Git, Docker, Vite, BeautifulSoup, Postman, WebSockets} \\
     \textbf{Machine Learning}{: Matplotlib, scikit-learn, TensorFlow, Keras}
    }}
 \end{itemize}

%---------- SOFT SKILLS ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Problem-Solving, Cross-Functional Collaboration, Agile Development, Technical Communication}}
 \end{itemize}

%-------------------------------------------
%%%%%%  CUSTOMIZATION GUIDE  %%%%%%%%%%%%%%%
%-------------------------------------------
% 
% TAILORING YOUR RESUME FOR SPECIFIC ROLES:
% 
% 1. REAL-TIME COLLABORATION / MODERN WEB (Notion, Figma, Miro):
%    Include: Daily Ledger, Final Year Portal, 3D Resume Builder
%    Focus: Real-time sync, PWA, collaborative features, Firebase
% 
% 2. WEB/MOBILE PLATFORMS (Meta, Google, Microsoft):
%    Include: Final Year Portal, Daily Ledger, 3D Resume Builder
%    Focus: Scale, modern frameworks, full-stack
% 
% 3. BACKEND/INFRASTRUCTURE (Amazon, Netflix):
%    Include: Wikipedia Path Finder, Final Year Portal, Daily Ledger
%    Focus: Optimization, caching, scalability
% 
% 4. FRONTEND/UI HEAVY (Adobe, Spotify, Airbnb):
%    Include: 3D Resume Builder, Daily Ledger, Final Year Portal
%    Focus: User experience, modern UI libraries, PWA
% 
% 5. ALGORITHMS/RESEARCH (DeepMind, OpenAI):
%    Include: Wikipedia Path Finder, Final Year Portal, 3D Resume Builder
%    Focus: Optimization metrics, problem-solving
% 
% 6. IoT/HARDWARE (Tesla, Apple Hardware):
%    Include: IoT Plant Watering, Daily Ledger, Final Year Portal
%    Uncomment the IoT project section above
% 
% 7. STARTUPS (Early-stage, Full-stack):
%    Include: All 4-5 projects if space permits
%    Shows versatility across hardware and software
% 
% KEY PROJECT STRENGTHS:
% - Daily Ledger: Real-time collaboration, PWA, Firebase, modern web
% - Final Year Portal: Scale, multi-role systems, production deployment
% - 3D Resume Builder: Creative problem-solving, WebSockets, Three.js
% - Wikipedia Path Finder: Algorithms, optimization, distributed systems
% - IoT Plant Watering: Hardware integration, full-stack IoT
% 
%-------------------------------------------

\end{document}