%-------------------------
% Resume in LaTeX
% Author: Yash Agarwal
% Template Based on: sb2nov/resume (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----- FORMATTING & MARGINS -----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----- SECTION FORMATTING -----
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----- ATS COMPATIBILITY -----
\pdfgentounicode=1

%----- CUSTOM COMMANDS -----
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\ % Changed this line
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}
    \end{tabular*}\vspace{-3pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Yash Agarwal} \\ \vspace{1pt}
    \small +91-90276-01476 $|$ \href{mailto:190e785@gmail.com}{190e785@gmail.com} $|$
    \href{https://in.linkedin.com/in/yash-agarwal-190e785}{\underline{linkedin.com/in/yash-agarwal-190e785}} $|$
    \href{https://github.com/190-785}{\underline{github.com/190-785}}
\end{center}

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era Hill University}{Uttarakhand, India}
      {B.Tech. in Computer Science \& Engineering; Honors in ML \& AI}{\textit{\small Aug 2023 -- Present}}
  \resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{May 2025 -- July 2025}
      {\href{https://drive.google.com/file/d/1yUwuZXi9aFgvmFDl0UV3BKAaYXMIYn_a/view?usp=sharing}{Arterns Technologies Private Limited}}{Dehradun, Uttarakhand}
      \resumeItemListStart
        \resumeItem{Developed and maintained user-facing features in React.js, ensuring cross-browser compatibility and responsive design.}
        \resumeItem{Translated Figma-based UI/UX mockups into high-quality, reusable React components using React Hooks and React Router.}
        \resumeItem{Integrated RESTful APIs and implemented asynchronous data flows to deliver real-time features such as chat and assessments.}
        \resumeItem{Optimized front-end performance, reducing load time by 18\% across devices and improving Lighthouse accessibility scores.}
        \resumeItem{Collaborated with designers, QA engineers, and back-end developers in Agile sprints, following CI/CD best practices via Azure DevOps.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}

  \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Plant_Watering_System}{IoT Automatic Plant Watering System}}}{Jun 2025 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} ESP8266, Firebase, C++, ESPAsyncWebServer}
        \resumeItem{Developed a secure web portal with responsive UI for Wi-Fi configuration and real-time monitoring.}
        \resumeItem{Integrated Firebase for token-based authentication and cloud data logging, enabling asynchronous remote access.}
        \resumeItem{Optimized system telemetry flow and data visualization for improved user experience and 20\% better watering efficiency.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/Interactive-Resume-Maker}{Interactive 3D Resume Builder}}}{Feb 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} React, Three.js, TypeScript, MongoDB, Spring Boot}
        \resumeItem{Built an interactive resume platform with reusable React components and responsive layouts optimized for multiple devices.}
        \resumeItem{Implemented JWT authentication and WebSocket-based collaboration, following modular CI/CD deployment pipelines.}
        \resumeItem{Delivered a unique front-end experience with cross-browser stability and measurable improvements in engagement.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{\href{https://github.com/190-785/First_Link_Backend}{Wikipedia Path Finder}}}{Oct 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Tech Stack:} Python, Flask, React, MongoDB, Docker}
        \resumeItem{Designed a React-based interface integrated with a Python/Flask backend, consuming REST APIs asynchronously.}
        \resumeItem{Optimized client-side rendering and caching, reducing API response latency by 80\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, Python, Java, C++} \\
     \textbf{Front-end}{: React.js, React Hooks, React Router, Next.js, HTML5, CSS3 (responsive \& cross-browser)} \\
     \textbf{Back-end \& APIs}{: Node.js, Flask, RESTful APIs, Asynchronous Programming} \\
     \textbf{Testing}{: Jest, React Testing Library} \\
     \textbf{CI/CD \& Cloud}{: Azure DevOps (Pipelines, Boards, Repos), Docker, GitHub Actions} \\
     \textbf{Databases}{: MongoDB, Firebase, Redis} 
    }}
 \end{itemize}

%---------- SOFT SKILLS ----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Agile/Scrum Methodologies, Collaboration, Problem-Solving, Debugging, Code Reviews}}
 \end{itemize}
 
\end{document}